#### The data

Working with two small data frames, `superheroes` and `publishers`.

```{r, message = FALSE, warning = FALSE}
library(tidyverse) ## dplyr provides the join functions

superheroes <- "
    name, alignment, gender,         publisher
 Magneto,       bad,   male,            Marvel
   Storm,      good, female,            Marvel
Mystique,       bad, female,            Marvel
  Batman,      good,   male,                DC
   Joker,       bad,   male,                DC
Catwoman,       bad, female,                DC
 Hellboy,      good,   male, Dark Horse Comics
"
superheroes <- read_csv(superheroes, skip = 1)

publishers <- "
  publisher, yr_founded
         DC,       1934
     Marvel,       1939
      Image,       1992
"
publishers <- read_csv(publishers, skip = 1)
```

#### inner_join(superheroes, publishers)

> inner_join(x, y): Return all rows from x where there are matching values in y, and all columns from x and y. If there are multiple matches between x and y, all combination of the matches are returned. This is a mutating join.

```{r}
(ijsp <- inner_join(superheroes, publishers))
```

We lose Hellboy in the join because, although he appears in `x = superheroes`, his publisher Dark Horse Comics does not appear in `y = publishers`. The join result has all variables from `x = superheroes` plus `yr_founded`, from `y`.

```{r include = FALSE}
superheroes_kable <- knitr::kable(superheroes)
publishers_kable <- knitr::kable(publishers)
ijsp_kable <- knitr::kable(ijsp)
```

::: {style="display: grid; grid-template-columns: 1fr 1fr 1fr; gap: 1rem; align-items: start;"}
```{r echo = FALSE}
superheroes_kable
```
```{r echo = FALSE}
publishers_kable
```
```{r echo = FALSE}
ijsp_kable
```
:::

#### Attribution

This is an excerpt of the STAT 545 `{dplyr}` joins cheatsheet created by Jenny Bryan. 
The entire original cheatsheet can be found here: <https://stat545.com/join-cheatsheet.html>.